Parameter Space Representation of Pareto Front to Explore Hardware-Software Dependencies

### 2014-07-23 algorithm.tex
added abstract, modified intro
typos
applied ACM style

\section{The algorithm}

@@

\item The avarage innovation score for the entire era is also calculated
as:
\[
is_{av,i}=\frac{is_{TOT,i}}{\left|\mathcal{R}_{i}\right|}
\]
where $\left|\mathcal{R}_{i}\right|$ is the number of regions of
era $i$ .
\item $\mathcal{R}_{i}$ is partitioned in three subsets (their meaning
will be discussed later):

@@

\subsection{Termination Condition}
The algorithm terminates at step $k$ if
\[
is_{TOT,k},is_{TOT,k-1},\dots,is_{TOT,k-\beta}\le\gamma\cdot is_{TOT,k-\left(\beta-1\right)}
\]
 where $\beta$ and $\gamma$ are selected by the experimenter (see
remark \ref{rem:termination}).
\begin{rem}
\label{pers02.rem:smaller_regions}The rule \ref{pers02.enu:K} of
the iteration rules says that the smaller is a region, the more ``crowded''
it is. It means that configurations in smaller regions are evaluated
with more ``attention'' (see figure \ref{pers02.fig:small_and_big}).

\begin{figure}[h]
\includegraphics[width=0.9\columnwidth]{img/small_and_big}

@@

\end{rem}

\begin{rem}
The rule \ref{pers02.enu:novelty_score_of_a_configuration} says that
a configuration whose objectives are more ``separated'' by the previous
Pareto front, has to be taken in greater account than others. A configuration
that is very near, in the objective space, to the previous Pareto
front doesn't add a true innovation. Therefore, the innovation score
of a configuration is a measure of how much interest we have in considering
it (see figure \ref{pers02.fig:Novelty-score-of-a-config}).

\begin{figure}[h]
\includegraphics[width=0.9\columnwidth]{img/novelty_score}

@@

\end{rem}

\begin{rem}
The innovation score of a region is a measure of how much different
are the points that it adds to Pareto Front compared to the previous
Pareto front. ``High innovation regions'' are the ones in which
more configurations are worth evaluating, because they add many points
on not yet well explored Pareto front areas. Therefore, these regions
are split in the next era (see remark \ref{pers02.rem:smaller_regions})
and more ``crowded'' by simulations. ``No innovation regions''
are the ones that have proved to add few points on Pareto fronts,
probably very near to previous Pareto front points and a Pareto front
point near to previous points is not so much interesting. Therefore
it's not worth evaluating many of their configurations and it is useful
to merge these regions, in order to less densely evaluate them.

@@

\end{rem}

\begin{rem}
\label{rem:termination}The algorithm terminates when in the last
$\beta$ iterations not a great ``amount of innovation'' has been
discovered. Therefore it is very probably that carrying on iterating
will not considerably change the Pareto front already formed. It's
not recommended to chose $\beta=1$, because it is possible that the
Pareto fronts $\mathbf{o}\left(\mathscr{P}_{k-1}\right)$ and $\mathbf{o}\left(\mathscr{P}_{k}\right)$
are not very different but next Pareto fronts could be. In other words,
it's unsafe to terminate as soon as the Pareto front doesn't change
enough between two consecutive eras, thus a strategy taking into
account the history of the Pareto fronts has been adopted in the
proposed approach.
\end{rem}
%!!! IN INGLESE E' PIU' CORRETTO DIRE: ``IT IS POSSIBLE THAT THE PARETO
%FRONTS WERE NOT VERY DIFFERENT''? (CON ``WERE'' AL POSTO DI ``ARE'')

\begin{rem}
Merging and splitting the regions are very dynamic processes. A portion
of the parameter space can be populated by a large number of small
regions in some eras, but can be covered by a small number of large
regions in next eras. This can be explained saying that, after a number
of eras of intense exploration of a portion of parameter space, this
exploration has turned to be enough thorough and so it was time for
other portions to be minutely scanned.
\end{rem}

>>>>

\section{The algorithm}
\label{sec:algorithm}

@@

\item The average innovation score for the entire era is also calculated
as:
\[
is_{av,i}=\frac{is_{TOT,i}}{\left|\mathcal{R}_{i}\right|}
\]
where $\left|\mathcal{R}_{i}\right|$ is the number of regions of
era $i$ .
\item $\mathcal{R}_{i}$ is partitioned in three subsets (their meaning
will be discussed later):

@@

\subsection{Termination Condition}
The algorithm terminates at step $k$ if
\[
is_{TOT,k},is_{TOT,k-1},\dots,is_{TOT,k-\beta}\le\gamma\cdot is_{TOT,k-\left(\beta-1\right)}
\]
 where $\beta$ and $\gamma$ are selected by the experimenter (see
remark \ref{rem:termination}).
\begin{remark}
\label{pers02.rem:smaller_regions}The rule \ref{pers02.enu:K} of
the iteration rules says that the smaller is a region, the more ``crowded''
it is. It means that configurations in smaller regions are evaluated
with more ``attention'' (see figure \ref{pers02.fig:small_and_big}).

\begin{figure}[h]
\includegraphics[width=0.5\columnwidth]{img/small_and_big}

@@

\end{remark}

\begin{remark}
The rule \ref{pers02.enu:novelty_score_of_a_configuration} says that
a configuration whose objectives are more ``separated'' by the previous
Pareto front, has to be taken in greater account than others. A configuration
that is very near, in the objective space, to the previous Pareto
front doesn't add a true innovation. Therefore, the innovation score
of a configuration is a measure of how much interest we have in considering
it (see figure \ref{pers02.fig:Novelty-score-of-a-config}).

\begin{figure}[h]
\includegraphics[width=0.5\columnwidth]{img/novelty_score}

@@

\end{remark}

\begin{remark}
The innovation score of a region is a measure of how much different
are the points that it adds to Pareto Front compared to the previous
Pareto front. ``High innovation regions'' are the ones in which
more configurations are worth evaluating, because they add many points
on not yet well explored Pareto front areas. Therefore, these regions
are split in the next era (see remark \ref{pers02.rem:smaller_regions})
and more ``crowded'' by simulations. ``No innovation regions''
are the ones that have proved to add few points on Pareto fronts,
probably very near to previous Pareto front points and a Pareto front
point near to previous points is not so much interesting. Therefore
it's not worth evaluating many of their configurations and it is useful
to merge these regions, in order to less densely evaluate them.

@@

\end{remark}

\begin{remark}
\label{rem:termination}The algorithm terminates when in the last
$\beta$ iterations not a great ``amount of innovation'' has been
discovered. Therefore it is very probably that carrying on iterating
will not considerably change the Pareto front already formed. It's
not recommended to chose $\beta=1$, because it is possible that the
Pareto fronts $\mathbf{o}\left(\mathscr{P}_{k-1}\right)$ and $\mathbf{o}\left(\mathscr{P}_{k}\right)$
are not very different but next Pareto fronts could be. In other words,
it's unsafe to terminate as soon as the Pareto front doesn't change
enough between two consecutive eras, thus a strategy taking into
account the history of the Pareto fronts has been adopted in the
proposed approach.
\end{remark}
%!!! IN INGLESE E' PIU' CORRETTO DIRE: ``IT IS POSSIBLE THAT THE PARETO
%FRONTS WERE NOT VERY DIFFERENT''? (CON ``WERE'' AL POSTO DI ``ARE'')

\begin{remark}
Merging and splitting the regions are very dynamic processes. A portion
of the parameter space can be populated by a large number of small
regions in some eras, but can be covered by a small number of large
regions in next eras. This can be explained saying that, after a number
of eras of intense exploration of a portion of parameter space, this
exploration has turned to be enough thorough and so it was time for
other portions to be minutely scanned.
\end{remark}

### 2014-07-23 concepts.tex
applied ACM style

\label{sec:statement_of_the_problem}\index{DSE}

@@

The {\em Pareto-optimal set} of $S$ for the application $b$ is the
set:
\[ \mathcal{P}(S,b) = \{ \mathbf{c} \in \mathcal{C}^*(S) \ : \nexists \ \mathbf{c}' \in \mathcal{C}^*(S), \mathbf{c}' \succ \mathbf{c} \} \]
that is, the set of configurations $\mathbf{c} \in
\mathcal{C}^*(S)$ not dominated by any other configuration.
Pareto-optimal configurations are configurations belonging to the
Pareto-optimal set and the {\em Pareto-optimal front} is the image
of the Pareto-optimal configurations, i.e. the set:
\[ \mathcal{P}_{F}(S,b) = \{ \mathbf{o} : \mathbf{o} = E(\mathbf{c},b), \mathbf{c} \in \mathcal{P}(S,b) \} \]

@@

\begin{figure}[h]
\includegraphics[width=0.9\columnwidth]{img/Pareto_set_and_front}

\caption{Relation between Pareto set (its ``parameter space representation'')
and Pareto front (``objective space representation'')}

\subsection{Required Definitions and Concepts}

@@

We also consider, in measuring how much iteresting a region is, the
``innovation'' that it adds. If, during a design space exploration,
a Pareto front is temporarily calculated, adding a new Pareto front
point near to the previous ones is not a considerable ``innovation'',
because the way it fulfils the objectives is very similar to other
already evaluated configurations. On the contrary, adding a new Pareto
front point that is very distant from previous ones is remarkable,
because it let the experimenter realize that the objectives can be
fulfilled in a completely different way from what he already found
during exploration. So a region will be evaluated ineresting as much
as how different are its added Pareto front points from the ones already
found.
\begin{rem}
We will consider only parameters $p_{i}$ with ordering, i.e. such
that, if $P_{i}$ is a domain, $\forall a,b\in P_{i}$ it is possible
to say $a<b$ or $a=b$ or $a>b$.
\end{rem}
%TODO: DESCRIVERE COME SI PENSA DI TRATTARE GLI SCENARI IN CUI ESISTONO
%PARAMETRI SENZA ORDINAMENTO{]}
\begin{defn}
\emph{Parameter interval}

Let $p_{i}$ be a parameter and $a_{i},b_{i}\in P_{i},a_{i}<b_{i}$.
A $p_{i}$- interval is
\[
\left[a_{i}..b_{i}\right]=\left[a_{i},b_{i}\right]\cap P_{i}
\]
 (i.e. taking the interval $\left[a_{i},b_{i}\right]$ , $\left[a_{i}..b_{i}\right]$
is the set of values of $P_{i}$ lying in $\left[a_{i},b_{i}\right]$)
\end{defn}

\begin{defn}
\emph{\label{pers02.def:Contiguous-intervals}Contiguous intervals}

Let $\left[a_{i}..b_{i}\right]$ and $\left[x_{i}..y_{i}\right]$
be two $p_{i}$-intervals. They are said to be contiguous iff
\begin{itemize}
\item $\left[a_{i}..b_{i}\right]\cap\left[x_{i}..y_{i}\right]=\emptyset$
and
\item $\left[a_{i}..b_{i}\right]\cup\left[x_{i}..y_{i}\right]$ is a $p_{i}$-
interval or $\left[x_{i}..y_{i}\right]\cup\left[a_{i}..b_{i}\right]$
is a $p_{i}$- interval
\end{itemize}
\end{defn}
\begin{figure}[h]
\includegraphics[width=0.9\columnwidth]{img/contiguous_intervals_or_not}

@@

\begin{defn}
\emph{Region}

A region is a set of the following form:
\[
R=\left[a_{1}..b_{1}\right]\times\dots\times\left[a_{n}..b_{n}\right]=\prod\left[a_{i}..b_{i}\right]
\]
 (see figure \ref{pers02.fig:Examples-of-regions})

\begin{figure}[h]
\includegraphics[width=0.9\columnwidth]{img/regions}

@@

\end{figure}
\end{defn}
\begin{rem}
We will talk later of ``big'' and ``small'' regions. The sense
of these terms is related to the cardinality of regions. A region
$R_{1}$ is said to be \emph{bigger }then $R_{2}$, if
\[
\left|R_{1}\right|>\left|R_{2}\right|
\]
 where $\left|R_{1}\right|$ and $\left|R_{2}\right|$ are the cardinalities
of $R_{1}$ and $R_{2}$. Similarly, a $p_{i}$-interval $\left[a_{i}..b_{i}\right]$
is said to be bigger then another $p_{i}$-interval $\left[c_{i}..d_{i}\right]$
if:
\[
\left|\left[a_{i}..b_{i}\right]\right|>\left|\left[c_{i}..d_{i}\right]\right|
\]

Therefore, the width of a $p_{i}$-interval $\left[a_{i}..b_{i}\right]$
is not given by the numeric value $b_{i}-a_{i}$ but it is its cardinality.
\end{rem}
We now provide some rules to split and merge regions. They will be
useful when explaining our proposed exploration algorithm.
\begin{defn}
\emph{\label{pers02.def:Splitting-a-region}Splitting a region}

If $\left[a_{i}..b_{i}\right]$ has more than one element, i.e. $\left|\left[a_{i}..b_{i}\right]\right|>1$,
it can be split in two contiguous intervals
\[
\left[a_{i}..c_{i}\right],\left[d_{i}..b_{i}\right]
\]
 such that
\[
\begin{cases}
\left[a_{i}..c_{i}\right]\cap\left[d_{i}..b_{i}\right] & =\emptyset\\
\left[a_{i}..c_{i}\right]\cup\left[d_{i}..b_{i}\right] & =\left[a_{i}..b_{i}\right]\\
\left|\left[a_{i}..c_{i}\right]\right| & =\left\lceil \frac{\left|\left[a_{i}..b_{i}\right]\right|}{2}\right\rceil 
\end{cases}
\]

@@

\begin{figure}[h]
\includegraphics[width=0.9\columnwidth]{img/splitting_the_region}

@@

\end{defn}

\begin{defn}
\emph{Contiguous regions}

Let $R_{1}=\prod\left[a_{i}\dots b_{i}\right]$ and $R_{2}=\prod\left[x_{i}..y_{i}\right]$
be two regions. They are said to be contiguous iff
\begin{itemize}
\item a $j$ exists such that $\left[a_{i}..b_{i}\right]=\left[x_{i}..y_{i}\right]$
for all $i\neq j$ 
\item $\left[a_{j}..b_{j}\right]$ and $\left[x_{j}..y_{j}\right]$ are
contiguous intervals (see definition \ref{pers02.def:Contiguous-intervals})
\end{itemize}
\end{defn}
See figure \ref{pers02.fig:Contiguous-regions}.

\begin{figure}[h]
\includegraphics[width=0.9\columnwidth]{img/contiguous_regions}

@@

\begin{defn}
\emph{\label{pers02.def:Merging-regions}Merging regions}

Let $R_{1}$ and $R_{2}$ be two contiguous regions as the previous
ones. Because of the definition of contiguous intervals, it is possible
that $b_{j}<x_{j}$ or $y_{j}<a_{j}$. We can merge the contiguous
intervals and obtain a new interval, as the following
\[
\left[t_{j},z_{j}\right]=\begin{cases}
\left[a_{j}..y_{j}\right] & \mbox{ if }b_{j}<x_{j}\\
\left[x_{j}..b_{j}\right] & \mbox{ if }y_{j}<a_{j}
\end{cases}
\]

@@

Such an $R$ will be indicated with the following notation:
\[
R=R_{1}+R_{2}
\]
\end{defn}
\begin{rem}
$R_{1}+R_{2}$ is mathematically equivalent to $R_{1}\cup R_{2}$.
However, using $R_{1}+R_{2}$ notation, we enforce the argument that
$R_{1}$ and $R_{2}$ must be to contiuguous regions.
\end{rem}

\begin{defn}
\emph{Separation}

Let $\mathbf{o}=\left(o_{1},\dots,o_{m}\right)$ and $\mathbf{q}=\left(q_{1},\dots,q_{m}\right)$
be two points of $O_{1}\times\dots\times O_{m}$. The separation between
$\mathbf{o}$ and $\mathbf{q}$ is 
\[
s\left(\mathbf{o}\rightarrow\mathbf{q}\right)=\sum_{i=1}^{m}\left|\frac{o_{i}-q_{i}}{o_{i}}\right|
\]

Notice that the separation is not a commutative operator.\end{defn}
\begin{rem}
The separation between $\mathbf{o}$ and $\mathbf{q}$ measures how
much we must vary $\mathbf{o}$ to transfrom it in $\mathbf{q}$.
The separation is a ``normalized'' measure that is independent of
the nature and the unit of measurement of the objectives
\end{rem}

\begin{defn}
\emph{Separation (alternative)}

Another definition of separation could be:
\[
s\left(\mathbf{o}\rightarrow\mathbf{q}\right)=\max_{i=1,\dots,m}\left|\frac{o_{i}-q_{i}}{o_{i}}\right|
\]

\end{defn}

>>>>

\label{sec:statement_of_the_problem}

@@

\begin{definition}[Pareto Set]
\label{pers02.def:Pareto-set}
The {\em Pareto-optimal set} of $S$ for the application $b$ is the
set:
\[ \mathcal{P}(S,b) = \{ \mathbf{c} \in \mathcal{C}^*(S) \ : \nexists \ \mathbf{c}' \in \mathcal{C}^*(S), \mathbf{c}' \succ \mathbf{c} \} \]
\end{definition}
that is, the set of configurations $\mathbf{c} \in
\mathcal{C}^*(S)$ not dominated by any other configuration.
Pareto-optimal configurations are configurations belonging to the
Pareto-optimal set and the {\em Pareto-optimal front} is the image
of the Pareto-optimal configurations, i.e. the set:
\[ \mathcal{P}_{F}(S,b) = \{ \mathbf{o} : \mathbf{o} = E(\mathbf{c},b), \mathbf{c} \in \mathcal{P}(S,b) \} \]

@@

\begin{figure}[h]
\includegraphics[width=0.5\columnwidth]{img/Pareto_set_and_front}
\caption{Relation between Pareto set (its ``parameter space representation'')
and Pareto front (``objective space representation'')}
\end{figure}

\subsection{Sketch of the Idea}

@@

We also consider, in measuring how much interesting a region is, the
``innovation'' that it adds. If, during a design space exploration,
a Pareto front is temporarily calculated, adding a new Pareto front
point near to the previous ones is not a considerable ``innovation'',
because the way it fulfils the objectives is very similar to other
already evaluated configurations. On the contrary, adding a new Pareto
front point that is very distant from previous ones is remarkable,
because it let the experimenter realize that the objectives can be
fulfilled in a completely different way from what he already found
during exploration. So a region will be evaluated interesting as much
as how different are its added Pareto front points from the ones already
found.

%TODO: sync name of values with formulation
\subsection{Required Definitions}
\begin{definition}[Parameter Interval] Let $p_{i}$ be a parameter and $a_{i},b_{i}\in P_{i},a_{i}<b_{i}$.
A $p_{i}$- interval is
\[
\left[a_{i}..b_{i}\right]=\left[a_{i},b_{i}\right]\cap P_{i}
\]
 (i.e. taking the interval $\left[a_{i},b_{i}\right]$ , $\left[a_{i}..b_{i}\right]$
is the set of values of $P_{i}$ lying in $\left[a_{i},b_{i}\right]$)
\end{definition}

\begin{remark}
We will consider only parameters $p_{i}$ with ordering, i.e. such
that, if $P_{i}$ is a domain, $\forall a,b\in P_{i}$ it is possible
to say $a<b$ or $a=b$ or $a>b$.
\end{remark}

%TODO: DESCRIVERE COME SI PENSA DI TRATTARE GLI SCENARI IN CUI ESISTONO
%PARAMETRI SENZA ORDINAMENTO{]}
\begin{definition}[Contiguous intervals]
\label{pers02.def:Contiguous-intervals}
Let $\left[a_{i}..b_{i}\right]$ and $\left[x_{i}..y_{i}\right]$
be two $p_{i}$-intervals. They are said to be contiguous iff
\begin{itemize}
\item $\left[a_{i}..b_{i}\right]\cap\left[x_{i}..y_{i}\right]=\emptyset$
and
\item $\left[a_{i}..b_{i}\right]\cup\left[x_{i}..y_{i}\right]$ is a $p_{i}$-
interval or $\left[x_{i}..y_{i}\right]\cup\left[a_{i}..b_{i}\right]$
is a $p_{i}$- interval
\end{itemize}
\end{definition}
\begin{figure}[h]
\includegraphics[width=0.5\columnwidth]{img/contiguous_intervals_or_not}

@@

\begin{definition}[Region]A region is a set of the following form:
\[
R=\left[a_{1}..b_{1}\right]\times\dots\times\left[a_{n}..b_{n}\right]=\prod\left[a_{i}..b_{i}\right]
\]
 (see figure \ref{pers02.fig:Examples-of-regions})

\begin{figure}[h]
\includegraphics[width=0.5\columnwidth]{img/regions}

@@

\end{figure}
\end{definition}

\begin{remark}
We will talk later of ``big'' and ``small'' regions. The sense
of these terms is related to the cardinality of regions. A region
$R_{1}$ is said to be \emph{bigger }then $R_{2}$, if
\[
\left|R_{1}\right|>\left|R_{2}\right|
\]
 where $\left|R_{1}\right|$ and $\left|R_{2}\right|$ are the cardinalities
of $R_{1}$ and $R_{2}$. Similarly, a $p_{i}$-interval $\left[a_{i}..b_{i}\right]$
is said to be bigger then another $p_{i}$-interval $\left[c_{i}..d_{i}\right]$
if:
\[
\left|\left[a_{i}..b_{i}\right]\right|>\left|\left[c_{i}..d_{i}\right]\right|
\]

Therefore, the width of a $p_{i}$-interval $\left[a_{i}..b_{i}\right]$
is not given by the numeric value $b_{i}-a_{i}$ but it is its cardinality.
\end{remark}

We now provide some rules to split and merge regions. They will be
useful when explaining our proposed exploration algorithm.
\begin{definition}[Splitting a region]
\label{pers02.def:Splitting-a-region}
If $\left[a_{i}..b_{i}\right]$ has more than one element, i.e. $\left|\left[a_{i}..b_{i}\right]\right|>1$,
it can be split in two contiguous intervals
\[
\left[a_{i}..c_{i}\right],\left[d_{i}..b_{i}\right]
\]
 such that
\[
\begin{cases}
\left[a_{i}..c_{i}\right]\cap\left[d_{i}..b_{i}\right] & =\emptyset\\
\left[a_{i}..c_{i}\right]\cup\left[d_{i}..b_{i}\right] & =\left[a_{i}..b_{i}\right]\\
\left|\left[a_{i}..c_{i}\right]\right| & =\left\lceil \frac{\left|\left[a_{i}..b_{i}\right]\right|}{2}\right\rceil 
\end{cases}
\]

@@

\begin{figure}[h]
\includegraphics[width=0.5\columnwidth]{img/splitting_the_region}

@@

\end{definition}

\begin{definition}[Contiguous regions]Let $R_{1}=\prod\left[a_{i}\dots b_{i}\right]$ and $R_{2}=\prod\left[x_{i}..y_{i}\right]$
be two regions. They are said to be contiguous iff
\begin{itemize}
\item a $j$ exists such that $\left[a_{i}..b_{i}\right]=\left[x_{i}..y_{i}\right]$
for all $i\neq j$ 
\item $\left[a_{j}..b_{j}\right]$ and $\left[x_{j}..y_{j}\right]$ are
contiguous intervals (see definition \ref{pers02.def:Contiguous-intervals})
\end{itemize}
\end{definition}
See figure \ref{pers02.fig:Contiguous-regions}.

\begin{figure}[h]
\includegraphics[width=0.5\columnwidth]{img/contiguous_regions}

@@

\begin{definition}[Merging regions]
\label{pers02.def:Merging-regions}
Let $R_{1}$ and $R_{2}$ be two contiguous regions as the previous
ones. Because of the definition of contiguous intervals, it is possible
that $b_{j}<x_{j}$ or $y_{j}<a_{j}$. We can merge the contiguous
intervals and obtain a new interval, as the following
\[
\left[t_{j},z_{j}\right]=\begin{cases}
\left[a_{j}..y_{j}\right] & \mbox{ if }b_{j}<x_{j}\\
\left[x_{j}..b_{j}\right] & \mbox{ if }y_{j}<a_{j}
\end{cases}
\]

@@

Such an $R$ will be indicated with the following notation:
\[
R=R_{1}+R_{2}
\]
\end{definition}

\begin{remark}
$R_{1}+R_{2}$ is mathematically equivalent to $R_{1}\cup R_{2}$.
However, using $R_{1}+R_{2}$ notation, we enforce the argument that
$R_{1}$ and $R_{2}$ must be to contiguous regions.
\end{remark}

\begin{definition}[Separation]Let $\mathbf{o}=\left(o_{1},\dots,o_{m}\right)$ and $\mathbf{q}=\left(q_{1},\dots,q_{m}\right)$
be two points of $O_{1}\times\dots\times O_{m}$. The separation between
$\mathbf{o}$ and $\mathbf{q}$ is 
\[
s\left(\mathbf{o}\rightarrow\mathbf{q}\right)=\sum_{i=1}^{m}\left|\frac{o_{i}-q_{i}}{o_{i}}\right|
\]
Notice that the separation is not a commutative operator.
\end{definition}

\begin{remark}
The separation between $\mathbf{o}$ and $\mathbf{q}$ measures how
much we must vary $\mathbf{o}$ to transform it in $\mathbf{q}$.
The separation is a ``normalized'' measure that is independent of
the nature and the unit of measurement of the objectives.
\end{remark}

\begin{definition}[Separation (alternative)] Another definition of separation could be:
\[
s\left(\mathbf{o}\rightarrow\mathbf{q}\right)=\max_{i=1,\dots,m}\left|\frac{o_{i}-q_{i}}{o_{i}}\right|
\]

\end{definition}

### 2014-07-23 paper_ieee.tex
applied ACM style

\newcommand{\comment}[1]{\textcolor{red}{AA: \bf #1}}
%\newcommand\comment[1]{} % When you enable this lines, all the notes will disappear

@@

\begin{IEEEkeywords}
DSE, VLIW, MultiObjective
\end{IEEEkeywords}
%------------------------------------------------------------------------------
\input{introduction.tex}
\input{concepts.tex}
\input{algorithm.tex}
\input{experiments.tex}
%------------------------------------------------------------------------------

\section{Conclusions}
This is the end

>>>>

%\newcommand{\comment}[1]{\textcolor{red}{AA: \bf #1}}
\newcommand\comment[1]{} % When you enable this lines, all the notes will disappear

@@

\begin{IEEEkeywords}
DSE, MultiObjective Optimization, Genetic Algorithms
\end{IEEEkeywords}
%------------------------------------------------------------------------------
\input{introduction.tex}
\input{concepts.tex}
\input{algorithm.tex}
\input{experiments.tex}
%------------------------------------------------------------------------------

\section{Conclusions}
In this work we presented a multiobjective strategy which 
introduces the concept of Parameter Space representation of Pareto
Set. A case study of a VLIW architecture involving strong
hardware/software dependencies has been carried out to evaluate
effectiveness with different amount of simulations budget.
A qualitative/quantitative comparison against a widespread multiobjective genetic
approach showed how the proposed strategy can result in a different
distribution of Pareto points which trades solutions granularity with
improved pareto extension.
